Triangulating iconicity: Coding analysis

### 2024-11-17 paper_01_consistency.Rmd
de-anonymized and re-rendered to check that everything still works

---
title: "Coding, consistency & calibration"
author: "[anonymized for review]"
date: "Updated `r format(Sys.Date())`"
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

```{r preliminaries, results="hide"}
# Packages
list.of.packages <- c("tidyverse","readxl","writexl","irr")
# new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
# if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only=T)

@@

write_xlsx(d.F.inconsistent,path="data/ideophones_F_consistency_2ndround.xlsx")

>>>>

---
title: "Coding, consistency & calibration"
author: "Mark Dingemanse, Stella Punselie, Bonnie McLean"
date: "Rendered `r format(Sys.Date())`"
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

```{r preliminaries, results="hide"}
# Packages
list.of.packages <- c("tidyverse","readxl","writexl","irr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only=T)

@@

#commented out to avoid overwriting
#write_xlsx(d.F.inconsistent,path="data/ideophones_F_consistency_2ndround.xlsx")

### 2024-11-17 paper_02_main_analyses.Rmd
de-anonymized and re-rendered to check that everything still works

---
title: "Triangulating iconicity: Coding analysis"
author: "[anonymised for review]"
date: "Updated `r format(Sys.Date())`"
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

Code notebook for a study of the relation between linguistically informed iconicity coding and experimentally collected guessability scores.

@@

## Data
Here we load the data. For earlier processing operations, see `paper_00_data_processing.R`.

@@

## Figures
Here we generate some descriptive stats and create the main figures for the paper. Note that Figures 1 and 2 in the paper are illustrative and their final versions are not generated in R.

@@

### Figure 2: Overview panel
The overview of the triangulation method is created separately in CorelDraw but we use the data from the guessability studies as a canvas.

@@

### Coding and guessability
As the visualizations already make clear there is a non-trivial positive relation between the presence of iconic mappings (in a cumulative sense) and the guessability score determined in experimental work.

@@

For the fixed effects, m1 lists a 0.182 improvement in logodds for C_cumulative. According to my interpretation this means that every added iconic feature leads to a ~7% boost in proportion correct.

@@

* `C_aspect`: 0.181 logodds (+7% boost)
* `C_modality`: 0.177 logodds (+7% boost)
* `C_length`: 0.443 logodds (+17% boost)

@@

* `C_length`: `r round(m8.estimates["C_length"],2)`
* `C_modality`: `r round(m8.estimates["C_modality"],2)`
* `C_aspect`: `r round(m8.estimates["C_aspect"],2)`

>>>>

---
title: "Triangulating iconicity: Coding analysis"
author: "Mark Dingemanse, Stella Punselie, Bonnie McLean"
date: "Updated `r format(Sys.Date())`"
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

Code notebook for a study of the relation between linguistically informed iconicity coding and experimentally collected guessability scores. Published paper is here:

Punselie, S., McLean, B., & Dingemanse, M. (2024). The Anatomy of Iconicity: Cumulative Structural Analogies Underlie Objective and Subjective Measures of Iconicity. *Open Mind*, 8, 1191–1212. doi: [10.1162/opmi_a_00162](https://doi.org/10.1162/opmi_a_00162)

@@

## Data

Here we load the data. For earlier processing operations, see `paper_00_data_processing.R`.

@@

## Figures

Here we generate some descriptive stats and create the main figures for the paper. Note that Figures 1 and 2 in the paper are illustrative and their final versions are not generated in R.

@@

### Figure 2: Overview panel

The overview of the triangulation method is created separately in CorelDraw but we use the data from the guessability studies as a canvas.

@@

### Coding and guessability

As the visualizations already make clear there is a non-trivial positive relation between the presence of iconic mappings (in a cumulative sense) and the guessability score determined in experimental work.

@@

For the fixed effects, m1 lists a 0.182 improvement in logodds for C_cumulative. According to my interpretation this means that every added iconic feature leads to a \~7% boost in proportion correct.

@@

-   `C_aspect`: 0.181 logodds (+7% boost)
-   `C_modality`: 0.177 logodds (+7% boost)
-   `C_length`: 0.443 logodds (+17% boost)

@@

-   `C_length`: `r round(m8.estimates["C_length"],2)`
-   `C_modality`: `r round(m8.estimates["C_modality"],2)`
-   `C_aspect`: `r round(m8.estimates["C_aspect"],2)`
